ext_risk_copula

### 2019-02-22 SuppMat.Rmd
renaming as suppmat

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Lewinton-Cohen model : $r=0$, Ricker model : $r\neq0$) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_ricker_risk_local_disp}](./Results/ricker/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Lewinton-Cohen model : $r=0$, Ricker model : $r\neq0$) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/ricker/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }

>>>>

![Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_ricker_risk_local_disp}](./Results/ricker/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years ; Ricker model with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/ricker/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }
